Reanalysis Step 3: Propensity Score Analysis with Twang

### 2025-08-17 reanalysis-3-propensity_scores.qmd
balance table bug

  # Store results
  twang_results[[i]] <- list(
    model = twang_model,
    weights = weights,
    ps_scores = twang_model$ps[, "es.mean"],
    n_trees_used = twang_model$desc$es.mean$n.trees,
    balance_es_mean = twang_model$balance$es.mean
  )

@@

for (i in 1:n_imputations) {
  # Get balance table from twang (es.mean only)
  bal_es <- twang_results[[i]]$balance_es_mean

  # Summary statistics for es.mean method
  balance_summaries[[i]] <- data.frame(
    Imputation = i,
    Mean_ES = mean(abs(bal_es$std.eff.sz), na.rm = TRUE),
    Max_ES = max(abs(bal_es$std.eff.sz), na.rm = TRUE),
    N_Imbalanced = sum(abs(bal_es$std.eff.sz) > 0.1, na.rm = TRUE),
    # KS statistics are still available in the es.mean balance table
    Mean_KS = mean(bal_es$ks, na.rm = TRUE),
    Max_KS = max(bal_es$ks, na.rm = TRUE)
  )
}

>>>>

  # Store results
  # When using single stop method, ps is a vector not a matrix
  ps_scores <- if(is.matrix(twang_model$ps)) {
    twang_model$ps[, "es.mean"]
  } else {
    twang_model$ps  # Already a vector when single stop method
  }

  # Get balance table - use summary or bal.table depending on what works
  balance_table <- tryCatch({
    # Try to get balance table
    if (!is.null(twang_model$balance.es.mean)) {
      twang_model$balance.es.mean
    } else if (!is.null(twang_model$balance)) {
      twang_model$balance
    } else {
      # Extract from summary
      summary(twang_model)$es.mean.ATT
    }
  }, error = function(e) {
    # If all else fails, create a simple balance assessment
    NULL
  })

  twang_results[[i]] <- list(
    model = twang_model,
    weights = weights,
    ps_scores = ps_scores,
    n_trees_used = twang_model$desc$es.mean$n.trees,
    balance_es_mean = balance_table
  )

@@

for (i in 1:n_imputations) {
  # Use summary to get balance statistics
  twang_summary <- summary(twang_results[[i]]$model)

  # The summary contains balance tables for es.mean.ATT
  if (!is.null(twang_summary$es.mean.ATT)) {
    bal_table <- twang_summary$es.mean.ATT

    # Extract effect sizes - look for appropriate columns
    es_values <- if ("tx.mn" %in% names(bal_table) && "ct.mn" %in% names(bal_table)) {
      # Calculate standardized differences manually if needed
      tx_means <- bal_table$tx.mn
      ct_means <- bal_table$ct.mn
      tx_sd <- if("tx.sd" %in% names(bal_table)) bal_table$tx.sd else rep(1, length(tx_means))
      ct_sd <- if("ct.sd" %in% names(bal_table)) bal_table$ct.sd else rep(1, length(ct_means))
      pooled_sd <- sqrt((tx_sd^2 + ct_sd^2) / 2)
      abs((tx_means - ct_means) / pooled_sd)
    } else if ("std.eff.sz" %in% names(bal_table)) {
      abs(bal_table$std.eff.sz)
    } else if ("std.es" %in% names(bal_table)) {
      abs(bal_table$std.es)
    } else {
      # Try to find any column with "std" or "es"
      std_cols <- grep("std|es", names(bal_table), value = TRUE)
      if (length(std_cols) > 0) {
        abs(bal_table[[std_cols[1]]])
      } else {
        rep(NA, nrow(bal_table))
      }
    }

    # Extract KS statistics if available
    ks_values <- if ("ks" %in% names(bal_table)) {
      bal_table$ks
    } else if ("ks.max" %in% names(bal_table)) {
      bal_table$ks.max
    } else {
      rep(NA, length(es_values))
    }

    balance_summaries[[i]] <- data.frame(
      Imputation = i,
      Mean_ES = mean(es_values, na.rm = TRUE),
      Max_ES = max(es_values, na.rm = TRUE),
      N_Imbalanced = sum(es_values > 0.1, na.rm = TRUE),
      Mean_KS = mean(ks_values, na.rm = TRUE),
      Max_KS = max(ks_values, na.rm = TRUE)
    )
  } else {
    # Fallback if summary doesn't have expected structure
    balance_summaries[[i]] <- data.frame(
      Imputation = i,
      Mean_ES = NA,
      Max_ES = NA,
      N_Imbalanced = NA,
      Mean_KS = NA,
      Max_KS = NA
    )
    message("Warning: Could not extract balance statistics for imputation ", i)
  }
}
